Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2022-01-05 paper/pge_appendix.Rmd
move y-axis countries in Fig1 to right

\pagebreak
```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
dcpo_input_raw_poliwork1 %>% 
  mutate(country = str_replace(country, "’", "'")) %>% 
    distinct(country, year, item, cc_rank) %>% 
    group_by(country, year) %>% 
    summarize(n = n(),
              cc_rank = cc_rank) %>% 
    ungroup() %>% 
    distinct() %>% 
    ggplot(aes(x = year, 
               y = forcats::fct_reorder(country, cc_rank),
               fill = n)) + 
    geom_tile() +
    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                      n.breaks = 7,
                      show.limits = TRUE,
                      right = FALSE,
                      name = "Observations") +
    labs(x = NULL, y = NULL) +
    scale_x_continuous(breaks=seq(1972, 2020, 4)) +
    theme(legend.justification=c(0, 0), 
          legend.position=c(0.01, 0.01),
          axis.text.y  = element_text(size = 7)) #+
    # ggtitle("Source Data Observations by Country and Year")
```

@@

dcpo_input_raw_poliwork1 %>% 
    group_by(country, year, item) %>%
    mutate(n = sum(n)) %>% 
    distinct(country, year, item, n) %>% 
    pivot_wider(names_from = "item", values_from = "n") %>% 
    ungroup() %>% 
    select(-country, -year) %>% 
    psych::pairwiseCount() %>% 
    as.data.frame() %>%
    rownames_to_column(var = "item") %>% 
    left_join(items_by_obs) %>%  
    arrange(-n_obs) %>% 
    select(item, any_of(items_by_obs %>% pull(item)), n_obs) %>% 
    pivot_longer(cols = matches("\\d.?$"), names_to = "var2", values_to = "count") %>%
    filter(count > 0) %>% 
    mutate(item = forcats::fct_reorder(item, n_obs),
           var2 = forcats::fct_relevel(var2, rev(levels(item)))) %>% 
    ggplot(aes(x = var2, 
               y = item,
               fill = count)) + 
    geom_tile() +
    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                      breaks = c(0, 1, 10, 20, 30, 50, 100),
                      show.limits = TRUE,
                      right = FALSE,
                      trans = "log10",
                      name = "Joint\nObservations") +
    labs(x = NULL, y = NULL) +
    theme(axis.text.x  = element_text(angle = 90, vjust = .5))

>>>>

\pagebreak
```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
dcpo_input_raw_poliwork1 %>% 
  mutate(country = str_replace(country, "’", "'")) %>% 
  distinct(country, year, item, cc_rank) %>% 
  group_by(country, year) %>% 
  summarize(n = n(),
            cc_rank = cc_rank) %>% 
  ungroup() %>% 
  distinct() %>% 
  ggplot(aes(x = year, 
             y = forcats::fct_reorder(country, cc_rank),
             fill = n)) + 
  geom_tile() +
  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                    n.breaks = 7,
                    show.limits = TRUE,
                    right = FALSE,
                    name = "Observations") +
  labs(x = NULL, y = NULL) +
  scale_x_continuous(breaks=seq(1972, 2020, 4)) +
  scale_y_discrete(position = "right") +
  theme(legend.justification=c(0, 0), 
        legend.position=c(0.01, 0.01),
        axis.text.y  = element_text(size = 7)) 
```

@@

dcpo_input_raw_poliwork1 %>% 
  group_by(country, year, item) %>%
  mutate(n = sum(n)) %>% 
  distinct(country, year, item, n) %>% 
  pivot_wider(names_from = "item", values_from = "n") %>% 
  ungroup() %>% 
  select(-country, -year) %>% 
  psych::pairwiseCount() %>% 
  as.data.frame() %>%
  rownames_to_column(var = "item") %>% 
  left_join(items_by_obs) %>%  
  arrange(-n_obs) %>% 
  select(item, any_of(items_by_obs %>% pull(item)), n_obs) %>% 
  pivot_longer(cols = matches("\\d.?$"), names_to = "var2", values_to = "count") %>%
  filter(count > 0) %>% 
  mutate(item = forcats::fct_reorder(item, n_obs),
         var2 = forcats::fct_relevel(var2, rev(levels(item)))) %>% 
  ggplot(aes(x = var2, 
             y = item,
             fill = count)) + 
  geom_tile() +
  scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                    breaks = c(0, 1, 10, 20, 30, 50, 100),
                    show.limits = TRUE,
                    right = FALSE,
                    trans = "log10",
                    name = "Joint\nObservations") +
  labs(x = NULL, y = NULL) +
  theme(axis.text.x  = element_text(angle = 90, vjust = .5))
```
